Modeling memory and taxis to analyze migrations

### 2021-02-07 code/StrategicVsTactical_PartI_v2.Rmd
edited R package code and minor changes to running model

```{r, message=FALSE, warning=FALSE}
source("functions2.R")
```

@@

eval <- FALSE
if(eval){
  MemSim <- runManyYears(World, Parameters = parameters, 
                         n.years = 3)
  save(MemSim, file = "../results/MemSim.rda")
} else load("../results/MemSim.rda")

par(mfrow = c(1,2), oma = c(0,0,3,0))
plotYearList(MemSim, tau = tau)
plotYearList(MemSim, tau = tau, persp = TRUE, scale = FALSE, expand = 100)
title(printParameters(parameters), outer = TRUE)
```

@@

eval <- FALSE
if(eval){
  FixedResourceSim <- runManyYears(world, Parameters = parameters, n.years = 3)
  save(FixedResourceSim, file = "../results/FixedResourceSim.rda")
} else load("../results/FixedResourceSim.rda")

par(mfrow = c(1,2), oma = c(0,0,3,0))
plotYearList(FixedResourceSim, tau = tau)
plotYearList(FixedResourceSim, tau = tau, persp = TRUE, scale = FALSE, expand = 100)
title(printParameters(parameters), outer = TRUE)
```

@@

eval <- FALSE
if(eval){
  MemResourceSim <- runManyYears(World, Parameters = parameters, n.years = 3)
  save(MemResourceSim, file = "../results/MemResourceSim.rda")
} else load("../results/MemResourceSim.rda")

par(mfrow = c(1,2), oma = c(0,0,3,0))
plotYearList(MemResourceSim, tau = tau)
plotYearList(MemResourceSim, tau = tau, persp = TRUE, scale = FALSE, expand = 100)
title(printParameters(parameters), outer = TRUE)
```

@@

```{r PulseSim1, fig.width = 10}
parameters <- c(epsilon = 5, alpha = 0, beta0 = 20, beta1 = 5e2)
Memory_PulsedResource_Sim <- runManyYears(world.R3, Parameters = parameters, n.years = 6)

par(mfrow = c(1,2), oma = c(0,0,3,0))
plotYearList(Memory_PulsedResource_Sim, tau = tau)
plotYearList(Memory_PulsedResource_Sim, tau = tau, persp = TRUE, scale = FALSE, expand = 100)
title(printParameters(parameters), outer = TRUE)
```

@@

```{r PulseSim2, fig.width = 10}
parameters <- c(epsilon = 2, alpha = 4e2, beta0 = 0, beta1 = 0)
Tactic_PulsedResource_Sim <- runManyYears(world.R1, Parameters = parameters, n.years = 6)

par(mfrow = c(1,2), oma = c(0,0,3,0))
plotYearList(Tactic_PulsedResource_Sim, tau = tau)
plotYearList(Tactic_PulsedResource_Sim, tau = tau, persp = TRUE, scale = FALSE, expand = 100)
title(printParameters(parameters), outer = TRUE)
```

@@

```{r PulseSim3, fig.width = 10}
parameters <- c(epsilon = 5, alpha = 2e2, beta0 = 20, beta1 = 3e2)
Hybrid_PulsedResource_Sim <- runManyYears(world.R1, Parameters = parameters, n.years = 6)

par(mfrow = c(1,2), oma = c(0,0,3,0))
plotYearList(Hybrid_PulsedResource_Sim, tau = tau)
plotYearList(Hybrid_PulsedResource_Sim, tau = tau, 
             persp = TRUE, scale = FALSE, expand = 100)
title(printParameters(parameters), outer = TRUE)
```

@@

```{r PulseSim4_tactic, fig.width = 10}
parameters <- c(epsilon = 2, alpha = 2e2, beta0 = 0, beta1 = 0)
Tactic_PulsedResource_Sim2 <- runManyYears(world.R1, Parameters = parameters, n.years = 6)

par(mfrow = c(1,2), oma = c(0,0,3,0))
plotYearList(Hybrid_PulsedResource_Sim2, tau = tau)
plotYearList(Hybrid_PulsedResource_Sim2, tau = tau, persp = TRUE, scale = FALSE, expand = 100)
title(printParameters(parameters), outer = TRUE)
```

@@

```{r PulseSim4_memory, fig.width = 10}
parameters <- c(epsilon = 5, alpha = 2e2, beta0 = 20, beta1 = 3e2)
Hybrid_PulsedResource_Sim3 <- runManyYears(world.R4, Parameters = parameters, n.years = 6)

par(mfrow = c(1,2), oma = c(0,0,3,0))
plotYearList(Hybrid_PulsedResource_Sim3, tau = tau)
plotYearList(Hybrid_PulsedResource_Sim3, tau = tau, persp = TRUE, scale = FALSE, expand = 100)
title(printParameters(parameters), outer = TRUE)
```

@@

```{r}
source("functions_indices.R")
  world$resource <- getPulsedResource(world$time, world$X, c(t.peak = 25, t.sd = 9, 
                                                             x.peak = 80, x.sd = 9))

  parameters <- c(epsilon = 5, alpha = 300, beta0=100, beta1 = 300)
  world.R1 <- world %>% 
    list_modify(resource = getPulsedResource(1:world$tau, world$X, 
                                             c(t.peak = 25, t.sd = 9, 
                                               x.peak = 80, x.sd = 9)))
  M <- runManyYears(world.R1, Parameters = parameters, n.years = 6)

  world.R1 <- world %>% list_modify(pop = M$Year6)
  M2 <- runManyYears(world.R1, Parameters = parameters, n.years = 6)

  source("functions_indices.R")
  indices1 <- sapply(M, computeIndices, resource = world$resource, world = world) %>% t
  indices2 <- sapply(M2, computeIndices, resource = world$resource, world = world) %>% t
  I <- rbind(indices1, indices2)

@@

>>>>

```{r, message=FALSE, warning=FALSE}
require("memorymigration")
```

@@

eval <- FALSE
if(eval){
  MemSim <- runManyYears(world, Parameters = parameters, 
                         n.years = 3, 0.99)
  save(MemSim, file = "../results/MemSim.rda")
} else load("../results/MemSim.rda")

par(mfrow = c(1,2), oma = c(0,0,3,0))
plotYearList(MemSim, world, tau = tau)
plotYearList(MemSim, world, tau = tau, persp = TRUE, scale = FALSE, expand = 100)
title(printParameters(parameters), outer = TRUE)
```

@@

eval <- FALSE
if(eval){
  FixedResourceSim <- runManyYears(world, Parameters = parameters, n.years = 3, 0.99)
  save(FixedResourceSim, file = "../results/FixedResourceSim.rda")
} else load("../results/FixedResourceSim.rda")

par(mfrow = c(1,2), oma = c(0,0,3,0))
plotYearList(FixedResourceSim, world, tau = tau)
plotYearList(FixedResourceSim, world, tau = tau, persp = TRUE, scale = FALSE, expand = 100)
title(printParameters(parameters), outer = TRUE)
```

@@

eval <- FALSE
if(eval){
  MemResourceSim <- runManyYears(world, Parameters = parameters, n.years = 3, 0.99)
  save(MemResourceSim, file = "../results/MemResourceSim.rda")
} else load("../results/MemResourceSim.rda")

par(mfrow = c(1,2), oma = c(0,0,3,0))
plotYearList(MemResourceSim, world, tau = tau)
plotYearList(MemResourceSim, world, tau = tau, persp = TRUE, scale = FALSE, expand = 100)
title(printParameters(parameters), outer = TRUE)
```

@@

```{r PulseSim1, fig.width = 10}
parameters <- c(epsilon = 5, alpha = 0, beta0 = 20, beta1 = 5e2)
Memory_PulsedResource_Sim <- runManyYears(world.R3, Parameters = parameters, n.years = 6, 0.99)

par(mfrow = c(1,2), oma = c(0,0,3,0))
plotYearList(Memory_PulsedResource_Sim, world.R3, tau = tau)
plotYearList(Memory_PulsedResource_Sim, world.R3, tau = tau, persp = TRUE, scale = FALSE, expand = 100)
title(printParameters(parameters), outer = TRUE)
```

@@

```{r PulseSim2, fig.width = 10}
parameters <- c(epsilon = 2, alpha = 4e2, beta0 = 0, beta1 = 0)
Tactic_PulsedResource_Sim <- runManyYears(world.R1, Parameters = parameters, n.years = 6, 0.99)

par(mfrow = c(1,2), oma = c(0,0,3,0))
plotYearList(Tactic_PulsedResource_Sim, world.R1, tau = tau)
plotYearList(Tactic_PulsedResource_Sim, world.R1, tau = tau, persp = TRUE, scale = FALSE, expand = 100)
title(printParameters(parameters), outer = TRUE)
```

@@

```{r PulseSim3, fig.width = 10}
parameters <- c(epsilon = 5, alpha = 2e2, beta0 = 20, beta1 = 3e2)
Hybrid_PulsedResource_Sim <- runManyYears(world.R1, Parameters = parameters, n.years = 6, 0.99)

par(mfrow = c(1,2), oma = c(0,0,3,0))
plotYearList(Hybrid_PulsedResource_Sim, world.R1, tau = tau)
plotYearList(Hybrid_PulsedResource_Sim, world.R1, tau = tau, 
             persp = TRUE, scale = FALSE, expand = 100)
title(printParameters(parameters), outer = TRUE)
```

@@

```{r PulseSim4_tactic, fig.width = 10}
parameters <- c(epsilon = 2, alpha = 2e2, beta0 = 0, beta1 = 0)
Tactic_PulsedResource_Sim2 <- runManyYears(world.R1, Parameters = parameters, n.years = 6, 0.99)

par(mfrow = c(1,2), oma = c(0,0,3,0))
plotYearList(Hybrid_PulsedResource_Sim2, world.R1, tau = tau)
plotYearList(Hybrid_PulsedResource_Sim2, world.R1, tau = tau, persp = TRUE, scale = FALSE, expand = 100)
title(printParameters(parameters), outer = TRUE)
```

@@

```{r PulseSim4_memory, fig.width = 10}
parameters <- c(epsilon = 5, alpha = 2e2, beta0 = 20, beta1 = 3e2)
Hybrid_PulsedResource_Sim3 <- runManyYears(world.R4, Parameters = parameters, n.years = 6, 0.99)

par(mfrow = c(1,2), oma = c(0,0,3,0))
plotYearList(Hybrid_PulsedResource_Sim3, world.R4, tau = tau)
plotYearList(Hybrid_PulsedResource_Sim3, world.R4, tau = tau, persp = TRUE, scale = FALSE, expand = 100)
title(printParameters(parameters), outer = TRUE)
```

@@

```{r}
dx <- 1

parameters <- c(epsilon = 5, alpha = 300, beta0=100, beta1 = 300)
world.R1 <- getSinePop(tau = 100, X.min = 0, X.max = 100, dx=2, 
                    peak.max = 80, peak.min = 20, sd = 10)
world.R1$resource <- getPulsedResource(world.R1$time, world.R1$X, c(t.peak = 25, t.sd = 9, 
                                                           x.peak = 80, x.sd = 9))

#run simulation for 12 years 
M <- runManyYears(world.R1, Parameters = parameters, n.years = 6, 1)

world.R2 <- world.R1 %>% list_modify(pop = M$Year6)
M2 <- runManyYears(world.R2, Parameters = parameters, n.years = 6, 1)

  indices1 <- sapply(M, computeIndices, resource = world.R1$resource, world = world.R1) %>% t
  indices2 <- sapply(M2, computeIndices, resource = world.R2$resource, world = world.R2) %>% t
  I <- rbind(indices1, indices2)

@@

```
Then we run the model to stop running the simulation at a certain threshold when the population reaches a "dynamic equilibrium state". In this example, the model only runs three years before hitting the threshold. 
```{r}
#simulation runs for 3 years since that is when threshold is hit

M <- runManyYears(world.R1, Parameters = parameters, n.years = 6, 0.99)
plotYearList(M, world.R1, tau = tau)

computeCohesiveness(M[[3]], world.R1)["SC.mean"]
computeMigratoriness(M[[3]], world.R1)$overlap
computeEfficiency(M[[3]], world.R1$resource, world.R1)
computeIndices(M[[3]], world.R1$resource, world.R1)
